Reanalysis Step 9: Alternative Propensity Score Specifications

### 2025-09-07 reanalysis-9-alternative_specifications.qmd
resiliency

# Define completed methods (add to this list as methods complete successfully)
completed_methods <- c(
  "nearest_glm",  # Uncomment if completed
  "nearest_gam"
  # "nearest_gbm",
  # "nearest_lasso",
  # "nearest_rpart",
  # "nearest_mahalanobis",
  # "subclass_glm",
  # "cbps",
  # "entropy",
  # "bart",
  # "twang_gbm"
)

# Methods to run = all methods minus completed ones
methods_to_run <- setdiff(all_methods, completed_methods)

# Optionally, you can also explicitly exclude problematic methods
methods_to_exclude <- c(
  # Add any methods that consistently fail or you want to skip
)
methods_to_run <- setdiff(methods_to_run, methods_to_exclude)

log_message(paste0("Will run ", length(methods_to_run), " methods"))
if (length(completed_methods) > 0) {
  log_message(paste0("Skipping completed: ", paste(completed_methods, collapse = ", ")))
}
```

@@

results <- run_alternative_ps_analysis(
  imputed_datasets = imputed_datasets,
  ps_formula = ps_formula,
  outcome_formula = outcome_formula,
  mode = analysis_mode,
  cache_dir = cache_dir,
  use_cache = use_cache,
  methods_to_run = methods_to_run
)

>>>>

# Force rerun flag - set to TRUE to reprocess all methods even if cached
force_rerun <- FALSE  # Set to TRUE to rerun everything

log_message(paste0("Will process up to ", length(all_methods), " methods"))
log_message(paste0("Force rerun: ", ifelse(force_rerun, "YES", "NO")))
```

@@

results <- run_alternative_ps_analysis(
  imputed_datasets = imputed_datasets,
  ps_formula = ps_formula,
  outcome_formula = outcome_formula,
  mode = analysis_mode,
  cache_dir = cache_dir,
  use_cache = use_cache,
  all_methods = all_methods,
  force_rerun = force_rerun  # Controls whether to reprocess cached results
)
